Comparative Analysis of Single--Neuron versus Dual--Neuron Output Layers in Binary Classification Neural Networks

### 2025-05-14 paper/model_architectures.tex
fixed latex issues

\begin{figure}[htbp]
\centering
\includegraphics[width=\textwidth]{figures/small_cnn_1neuron_architecture.png}
\caption{Small CNN architecture with single-neuron output layer. The network consists of three convolutional blocks followed by fully connected layers and a single sigmoid output neuron.}
\label{fig:small_cnn_arch_single}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=\textwidth]{figures/small_cnn_2neuron_architecture.png}
\caption{Small CNN architecture with dual-neuron output layer. The network maintains the same structure as the single-neuron variant but uses two output neurons with softmax activation.}
\label{fig:small_cnn_arch_dual}
\end{figure}

@@

\subsubsection{ResNet50 Architecture}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\textwidth]{figures/resnet50_1neuron_architecture.png}
\caption{ResNet50 architecture with single-neuron output layer. The model utilizes pre-trained weights from ImageNet, with only the final residual block and classifier layers fine-tuned for our binary classification tasks.}
\label{fig:resnet50_arch_single}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=\textwidth]{figures/resnet50_2neuron_architecture.png}
\caption{ResNet50 architecture with dual-neuron output layer. The model maintains the same structure as the single-neuron variant but uses two output neurons with softmax activation.}
\label{fig:resnet50_arch_dual}
\end{figure}

@@

\subsubsection{Vision Transformer (ViT) Architecture}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\textwidth]{figures/vit_1neuron_architecture.png}
\caption{Vision Transformer (ViT) architecture with single-neuron output layer. The model divides the input image into patches, processes them through transformer encoder blocks, and uses the class token representation for classification.}
\label{fig:vit_arch_single}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=\textwidth]{figures/vit_2neuron_architecture.png}
\caption{Vision Transformer (ViT) architecture with dual-neuron output layer. The model maintains the same structure as the single-neuron variant but uses two output neurons with softmax activation.}
\label{fig:vit_arch_dual}
\end{figure}

@@

\subsubsection{Output Layer Configurations}

>>>>

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.9\textwidth]{figures/small_cnn_1neuron_architecture.png}
\caption{Small CNN architecture with single-neuron output layer. The network consists of three convolutional blocks followed by fully connected layers and a single sigmoid output neuron.}
\label{fig:small_cnn_arch_single}
\end{figure}

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.9\textwidth]{figures/small_cnn_2neuron_architecture.png}
\caption{Small CNN architecture with dual-neuron output layer. The network maintains the same structure as the single-neuron variant but uses two output neurons with softmax activation.}
\label{fig:small_cnn_arch_dual}
\end{figure}

@@

\FloatBarrier
\subsubsection{ResNet50 Architecture}

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.9\textwidth]{figures/resnet50_1neuron_architecture.png}
\caption{ResNet50 architecture with single-neuron output layer. The model utilizes pre-trained weights from ImageNet, with only the final residual block and classifier layers fine-tuned for our binary classification tasks.}
\label{fig:resnet50_arch_single}
\end{figure}

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.9\textwidth]{figures/resnet50_2neuron_architecture.png}
\caption{ResNet50 architecture with dual-neuron output layer. The model maintains the same structure as the single-neuron variant but uses two output neurons with softmax activation.}
\label{fig:resnet50_arch_dual}
\end{figure}

@@

\FloatBarrier
\subsubsection{Vision Transformer (ViT) Architecture}

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.9\textwidth]{figures/vit_1neuron_architecture.png}
\caption{Vision Transformer (ViT) architecture with single-neuron output layer. The model divides the input image into patches, processes them through transformer encoder blocks, and uses the class token representation for classification.}
\label{fig:vit_arch_single}
\end{figure}

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.9\textwidth]{figures/vit_2neuron_architecture.png}
\caption{Vision Transformer (ViT) architecture with dual-neuron output layer. The model maintains the same structure as the single-neuron variant but uses two output neurons with softmax activation.}
\label{fig:vit_arch_dual}
\end{figure}

@@

\FloatBarrier
\subsubsection{Output Layer Configurations}
